Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/adversary.tex
add constant to real time formula, begin working on minerva vs prov example
changed property to Strategy-Proof

\begin{definition}
Let $d \in \{0, a\}$ stand for the null or the alternative hypothesis respectively.
Let $s_{i, d, [n_1, \ldots, n_r]}$ be the probability of observing $i$ ballots for the winner at the end of the $r^{th}$ round of an audit with round schedule $[n_1, \ldots, n_r]$ conditioned on hypothesis $H_d$ \textit{i.e.,} 
\[
s_{i, d, [n_1, \ldots, n_r]} = P\left[K_r = i | (n_1, \ldots, n_r), H_d\right]. 
%  = s_{i, d, [n_r]},
\]
For $r = 1$ 
\[
 s_{i, d, [n_r]} = \mathsf{Bin}(n_r, p_d, i).
\]
\end{definition}

\begin{example}[Adaptive round size selection] 
Let us assume a malicious auditor with the following strategy for \Minerva audit:
\begin{itemize}
 \item select round size $n_2$ if $k = k^* = k^{p_a, p_0, \alpha}_{min, 1} - 1$,
 \item select round size $n'_2$ for $k \leq k^{p_a, p_0, \alpha}_{min, 1} - 2$.
\end{itemize}
This leads to the situation that computed values of $r_{i, d}$ are not correct anymore \textit{i.e.,} value $s_{k^*}$ is missing for probabilities that go into $n'_2$.

@@

\begin{definition}[Strong RLA]
 An audit $\mathcal{A}$ is a Strong Risk Limiting Audit with risk limit $\alpha$ iff for
 all strategies of selecting round schedule and for sample $X$ 
 \[
  \Pr\left[\mathcal{A}(X) = \text{Correct} | H_0\right] \leq \alpha.
 \]

@@

\begin{lemma}
\Providence is Strong RLA. 
\end{lemma}
\begin{proof}
 The property comes as a conclusion of Theorem~\ref{thm:minerva2_is_rla_new} and Lemma~\ref{lemma:markov}.
\end{proof}

>>>>

\begin{definition}
Let $d \in \{0, a\}$ stand for the null or the alternative hypothesis respectively.
Let $s_{i, d, [n_1, \ldots, n_r]}$ be the probability of observing $i$ ballots for the winner after drawing the $r^{th}$ round of an audit with round schedule $[n_1, \ldots, n_r]$ conditioned on hypothesis $H_d$ \textit{i.e.,} 
\[
s_{i, d, [n_1, \ldots, n_r]} = P\left[K_r = i | (n_1, \ldots, n_r), H_d\right]. 
%  = s_{i, d, [n_r]},
\]
For $r = 1$ 
\[
 s_{i, d, [n_r]} = \mathsf{Bin}(n_r, p_d, i).
\]
\end{definition}

\begin{example}[Adaptive round size selection] 
Let us assume a malicious auditor with the following strategy for \Minerva audit:
\begin{itemize}
 \item select second round size $n_2$ if $k_{1} = k^* = k^{p_a, p_0, \alpha}_{min, 1} - 1$,
 \item select round size $n'_2$ for $k_1 \leq k^{p_a, p_0, \alpha}_{min, 1} - 2$.
\end{itemize}
This leads to the situation where the true value of $s_{i, d, [n_1, n_2]}$ is missing any contributions from $K_1=k^*$.

@@

\begin{definition}[Strategy-Proof RLA]
 An audit $\mathcal{A}$ is a Strategy-Proof Risk Limiting Audit with risk limit $\alpha$ iff for
 all strategies of selecting round schedule and for sample $X$ 
 \[
  \Pr\left[\mathcal{A}(X) = \text{Correct} | H_0\right] \leq \alpha.
 \]

@@

\begin{lemma}
\Providence is a Strategy-Proof RLA. 
\end{lemma}
\begin{proof}
This property follow from Theorem~\ref{thm:minerva2_is_rla_new} and Lemma~\ref{lemma:markov}.
\end{proof}

% To see the practical implication of this result, we consider a toy example: an RLA of a two-candidate contest with margin $10\%$ and risk limit $10\%$. 
% Suppose a first round of $100$ ballots is drawn and $60$ ballots in the sample are votes for the announced winner. Since $\tau_1(k,p_a,p_0,\ldots$...
